Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Changed modeling for modelling on the entire manuscript
Because gji requests British English, we must use "modelling"
instead of the American "modeling".

The lithosphere's density variation with depth has been studied for close to a
century.
Over this time period,
several density-depth relations have been proposed for different rock types
\citep[e.g.,][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, depth-variable densities have been used in forward and
inverse gravity modeling, mostly applied to sedimentary basins
\citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001,
Welford2010}.
These forward gravity models have been developed for two or three dimensional
bodies in Cartesian coordinates, which limits the applications to local scales.
The advent of satellite gravimetry has provided gravity field
measurements with global coverage, enabling modelling and interpretation on regional and
global scales.
Hence, designing forward modeling methods that reproduce the gravity anomalies for
such scales is of high importance.

To take into account the curvature of the Earth, many global forward modeling methods
are defined in geocentric spherical coordinates.
A common approach is to discretize the Earth into tesseroids (spherical prisms),
which are defined by pairs of latitude, longitude, and
radial boundaries (see Fig.~\ref{fig:tesseroid}).
The gravitational fields generated by an arbitrary
tesseroid on any external point are given by volume
integrals that are generally approximated by numerically.
The literature offers two main approaches: one involves Taylor series expansion
\citep{Heck2007, Grombein2013} while the other makes use of Gauss-Legendre
Quadrature (GLQ)
\citep{Asgharzadeh2007, Wild-Pfeiffer2008, Li2011, Uieda2016}.
The Taylor series expansion is not well suited to develop an algorithm for
a density varying with depth according to an arbitrary function.
Different series expansion terms would have to obtained for each density function
desired.
Conversely, an arbitrary density function can be included in the GLQ without
any change to the integration method.

>>>>

The lithosphere's density variation with depth has been studied for close to a
century.
Over this time period,
several density-depth relations have been proposed for different rock types
\citep[e.g.,][]{Maxant1980, Rao1986, Rao1993, Rao1994}.
Furthermore, depth-variable densities have been used in forward and
inverse gravity modelling, mostly applied to sedimentary basins
\citep{Cordell1973, Rao1986, Cowie1990, Rao1993, Rao1994, Zhang2001,
Welford2010}.
These forward gravity models have been developed for two or three dimensional
bodies in Cartesian coordinates, which limits the applications to local scales.
The advent of satellite gravimetry has provided gravity field
measurements with global coverage, enabling modelling and interpretation on regional and
global scales.
Hence, designing forward modelling methods that reproduce the gravity anomalies for
such scales is of high importance.

To take into account the curvature of the Earth, many global forward modelling methods
are defined in geocentric spherical coordinates.
A common approach is to discretize the Earth into tesseroids (spherical prisms),
which are defined by pairs of latitude, longitude, and
radial boundaries (see Fig.~\ref{fig:tesseroid}).
The gravitational fields generated by an arbitrary
tesseroid on any external point are given by volume
integrals that are generally approximated by numerically.
The literature offers two main approaches: one involves Taylor series expansion
\citep{Heck2007, Grombein2013} while the other makes use of Gauss-Legendre
Quadrature (GLQ)
\citep{Asgharzadeh2007, Wild-Pfeiffer2008, Li2011, Uieda2016}.
The Taylor series expansion is not well suited to develop an algorithm for
a density varying with depth according to an arbitrary function.
Different series expansion terms would have to obtained for each density function
desired.
Conversely, an arbitrary density function can be included in the GLQ without
any change to the integration method.
